Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-22 paper_quarto.qmd
footnote added

As mentioned earlier, the digitized text of "Natural History" with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted additional scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping code can be found in the link: .

@@

In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of \"India\".

>>>>

As mentioned earlier, the digitized text of "Natural History" with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted additional scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping was conducted with [beautifulsoup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in python, the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20scrape.ipynb) can be referred by click.[^1]

[^1]: Since the paper is a pilot exploration of my master thesis, I used the scraped corpus already scraped with python.

@@

In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of "India".
